Security Audit of Safeplug ``Tor in a Box''

### 2014-03-06 w2sp/report.tex
shortening the paper

\section{Related Work}
To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However there has been much prior research on the primary technology that the device uses: Tor.  Additionally, the security vulnerabilities that Safeplug attempts to secure users against have been previously studied in great detail; these include fingerprinting and cookies.

@@

{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.  Mayer and Mitchell survey recent policy and technology stances on web tracking; while tracking allows for free web content and innovation, it compromises a user's privacy~\cite{commercial2}.  They discuss the existence and use of stateful tracking by using ``supercookies.''  While many companies use cookies, there has also been work in developing privacy-preserving third-party services, such as Privad, Adnostic, and RePriv~\cite{guha, toubiana, fredrikson}.

>>>>

\section{Related Work}
To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However there has been much prior research on the primary technology that the device uses: Tor.  Additionally, a security vulnerability that Safeplug attempts to secure users against has been previously studied in great detail: fingerprinting.

@@

%{\bf Cookies} There has been much policy and technology debate around the topic of third-party web tracking.  Mayer and Mitchell survey recent policy and technology stances on web tracking; while tracking allows for free web content and innovation, it compromises a user's privacy~\cite{commercial2}.  They discuss the existence and use of stateful tracking by using ``supercookies.''  While many companies use cookies, there has also been work in developing privacy-preserving third-party services, such as Privad, Adnostic, and RePriv~\cite{guha, toubiana, fredrikson}.
